Miniproject - Elliptic Curves

### 2022-03-13 Elliptic Curves/submission.tex
Done part of 2(ii)

\begin{example}[1(ii)]
    Let
    \begin{equation*}
        \alpha = 5^{-1} + 2 \cdot 5^0 + 5 (1 + 4 \cdot 5) \sum_{n \geq 0} 5^{2n} \in \Q_5
    \end{equation*}
    Note that in $\Q_5$ we have
    \begin{equation*}
        \sum_{n \geq 0} 5^{2n} = \sum_{n \geq 0} 25^n = \frac 1 {1 - 25} = -\frac 1 {24}
    \end{equation*}
    So
    \begin{equation*}
        \alpha = \frac 1 5 + 2 + 5 (21) \frac 1 {24} = \frac {263} {40}
    \end{equation*}
\end{example}
For the next exercises, we will slightly abuse notation and write
\begin{equation*}
    E(R) := \{ (x, y) \in E \ | \ x, y \in R \}
\end{equation*}
for an Elliptic Curve $E$ defined over $k$ and any ring $R$ contained in some extension field of $k$.
\begin{prop}[1(iii)]
    Consider the Elliptic Curve $E: y^2 = x^3 + 2x + 2$ defined over $\Z$.
    Then $E(\Z) = \{ \O \}$ and
    \begin{equation*}
        E(\Z_p) \neq \{ \O \} \ \Leftrightarrow \ p \neq 3
    \end{equation*}
\end{prop}
\begin{proof}
    First show that there exists some $(x, y) \in \tilde{E}(\F_p)$ with $y \neq 0$ for all primes $p \neq 3$.

@@

    Consider now $P = (-2, 2) \in E$.
    The tangent at $P$ is given by $y = -x$ and the third point of intersection with $E$ is thus $(0, 0)$.
    Hence $P + P = (0, 0)$ and so $[4]P = \O$.
    It follows that $\#E_{\mathrm{tors}}(\Q) = 8$ and furthermore that 
    \begin{equation*}
        E_{\mathrm{tors}}(E) = \langle P, (-1, 0) \rangle \cong \Z/4\Z \oplus \Z/2\Z
    \end{equation*}
\end{example}

\printbibliography
\end{document}

>>>>

\begin{example}[1(ii)]
    Let
    \begin{equation*}
        \alpha = 5^{-1} + 2 \cdot 5^0 + 5 (1 + 4 \cdot 5) \sum_{n \geq 0} 5^{2n} \in \Q_5
    \end{equation*}
    Note that in $\Q_5$ we have
    \begin{equation*}
        \sum_{n \geq 0} 5^{2n} = \sum_{n \geq 0} 25^n = \frac 1 {1 - 25} = -\frac 1 {24}
    \end{equation*}
    So
    \begin{equation*}
        \alpha = \frac 1 5 + 2 + 5 (21) \frac 1 {24} = \frac {263} {40}
    \end{equation*}
\end{example}
For the next exercises, we will slightly abuse notation and write
\begin{equation*}
    E(R) := \{ (x, y) \in E(\bar{k}) \ | \ x, y \in R \} \cup \{\O\}
\end{equation*}
for an Elliptic Curve $E$ defined over $k$ and any ring $R$ contained in the algebraic closure $\bar{k}$.
Note that this is usually not a group anymore, and does not have a lot of nice structure.
\begin{prop}[1(iii)]
    Consider the Elliptic Curve $E: y^2 = x^3 + 2x + 2$ defined over $\Z$.
    Then $E(\Z) = \{ \O \}$ and
    \begin{equation*}
        E(\Z_p) \neq \{ \O \} \ \Leftrightarrow \ p \neq 3
    \end{equation*}
\end{prop}
\begin{proof}
    First show that there exists some $(x, y) \in \tilde{E}(\F_p)$ with $y \neq 0$ for all primes $p \neq 3$.

@@

    Consider now $P = (-2, 2) \in E$.
    The tangent at $P$ is given by $y = -x$ and the third point of intersection with $E$ is thus $(0, 0)$.
    Hence $P + P = (0, 0)$ and so $[4]P = \O$.
    It follows that $\#E_{\mathrm{tors}}(\Q) = 8$ and furthermore that 
    \begin{equation*}
        E_{\mathrm{tors}}(E) = \langle P, (-1, 0) \rangle \cong \Z/4\Z \oplus \Z/2\Z
    \end{equation*}
\end{example}
\begin{example}
    Consider the Elliptic Curve $E: y^2 = x(x + 1)(x - 8)$.
    Note that we have an isomorphism
    \begin{equation*}
        \psi: E \to E', \quad (x, y) \mapsto \left( x - \frac 7 3, y \right)
    \end{equation*}
    to the Elliptic Curve $E': y^2 = x^3 - \frac {73} 3 x - \frac {1190} {27}$ defined over $\Q$.
    Have that
    \begin{equation*}
        \Delta(E) = -72^2 = -5184 = \Delta(E')
    \end{equation*}
    Note that this has only the prime factors $2$ and $3$.
    As before, this shows that all the results from the lecture on the reduction modulo $p \neq 2, 3$ are also valid for the curve $E$, even though it is not defined by an equation of the form $y^2 = x^3 + Ax + B$.
    We see that
    \begin{equation*}
        \tilde{E}(\F_7) = \{ (0, 0), (1, 0), (4, 2), (4, 5), (5, 1), (5, 6), (6, 0), \O \}
    \end{equation*}
    and thus has order 8.
    As before, we this only leaves two possible cases, either the obvious 2-torsion points are all torsion points (i.e. $\#E_{\mathrm{tors}}(\Q) = 4$) or each of the points $\tilde{E}(\F_5)$ lifts to a torsion point (i.e. $\#E_{\mathrm{tors}}(\Q) = 8$).

    Unlike the previous example however, this time the former is the case.
    To see this, we use the Nagell-Lutz theorem.
    Assume $(x, y) \in E_{\mathrm{tors}}(\Q)$ with $y \neq 0$.
    Then it yields that $y^2 \divides \Delta(E) = -72^2$ and so $y \divides 72$.
    So
    \begin{equation*}
        y \in \{ \pm 1, \pm 2, \pm 4, \pm 8, \pm 3 \pm 6, \pm 12, \pm 24, \pm 9, \pm 18, \pm 36, \pm 72 \}
    \end{equation*}
    Furthermore $y \not\equiv 0 \mod 7$ and since $(\tilde{x}, \tilde{y}) \in \tilde{E}(\F_7)$, it follows that
    \begin{equation*}
        (\tilde{x}, \tilde{y}) \in \{ (4, \pm 2), (5, \pm 1) \} \ \Rightarrow \ \tilde{y} \in \{ \pm 1, \pm 2 \}
    \end{equation*}
    Thus we only have the possibilities
    \begin{equation*}
        y \in \{ \pm 1, \pm 2, \pm 8, \pm 6, \pm 12, \pm 9, \pm 36, \pm 72 \}
    \end{equation*}
    Furthermore, observe that
    \begin{equation*}
        \tilde{E}(\F_{11}) = \{ (0, 0), (5, 3), (5, 8), (6, 2), (6, 9), (8, 0), (10, 0), \O \}
    \end{equation*}
    and so it follows by the same argument that
    \begin{equation*}
        \tilde{y} \in \{ \pm 2, \pm 3 \}
    \end{equation*}
    This further restricts the possibilities to
    \begin{equation*}
        y \in \{ \pm 2, \pm 8, \pm 12, \pm 9 \}
    \end{equation*}
    Finally, observe that none of the equations
    \begin{align*}
        4 &= x^3 - 7x^2 - 8x \\
        64 &= x^3 - 7x^2 - 8x \\
        144 &= x^3 - 7x^2 - 8x \\
        81 &= x^3 - 7x^2 - 8x
    \end{align*}
    has a solution in $\Q$.
    To see this, use e.g. the rational root theorem and some computation:

    The only factors of $4$ are $\pm 1, \pm 2, \pm 4$ and none solves $4 = x^3 + 7x^2 - 8x$.
    The only factors of $64$ are $\pm 1, \pm 2, \pm 4, \pm 8, \pm 16, \pm 32, \pm 64$ and none solves $64 = x^3 - 7x^2 - 8x$.
    The only factors of $144$ are $\pm 1, \pm 2, \pm 4, \pm 8, \pm 16, \pm 3, \pm 6, \pm 12, \pm 24, \pm 48, \pm 9, \pm 18, \pm 36, \pm 72, \pm 144$ and none solves $144 = x^3 - 7x^2 - 8x$.
    The only factors of $81$ are $\pm 1, \pm 3, \pm 9, \pm 27, \pm 81$ and none solves $81 = x^3 - 7x^2 - 8x$.
\end{example}
\end{document}
